---
title: "28DEGMC_TRAVEL_Q"
author: "Kuljeet"
date: "6/19/2023"
output: html_document
---

```{r, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DBI)
library(dplyr)
library(dbplyr)
library(odbc)
library(DT)
library(tidyverse)
library(data.table)
library(waterfalls)
library(ggplot2)
library(janitor)
library(scales)
library (sqldf)
library(ggthemes)
library(plyr)

```


```{r}
readRenviron(".Renviron") 


database <- "PD_CUSTOMER_ANALYTICS"
myconn <- DBI::dbConnect(odbc::odbc(), "SNOWFLAKEC360", 
                         database = "PD_CUSTOMER_ANALYTICS", 
                         uid = if(Sys.getenv('SNOWFLAKE_UID') != "") Sys.getenv('SNOWFLAKE_UID') else NULL,
                         token = if(Sys.getenv('SNOWFLAKE_C360_TOKEN') != "") Sys.getenv('SNOWFLAKE_C360_TOKEN') else NULL)

```

#### Waterfall report for 28DEGMC MARKETABLE BASE 

```{sql connection=myconn, output.var = "DEGREES28_MKT_BASE"}

SELECT 
  X1.CUST_ACCT_APPL_ID
  ,X1.CRM_PRODUCT
  ,X1.CRM_ACCOUNT_ACTIVE_FLAG
   ,X1.FIRST_NAME
  ,X1.EMAILADDRESS
  ,X3.STATUSCURR
  ,X1.GENDER
  ,X3.CRM_MOB
  ,ROUND(X1.CREDITLIMIT_AMT) AS CREDITLIMIT
  ,X1.CURR_BAL_AMT
  ,X3.CRM_OTB_AMT
  ,X2.MARKETABLE_CARDS_FLAG
  ,X2.DNS_CLVLE_DIGITAL_FLAG 
  ,X2.ACMA_OPTIN 
  ,X2.SPAMHAUS_OPTIN 
  ,CASE WHEN ((X1.CREDITLIMIT_AMT - X1.CURR_BAL_AMT <= 300)) THEN 1 ELSE 0 END AS OTB_LESSTHAN_300
  ,CASE WHEN (X1.FIRST_NAME IS NULL or X1.EMAILADDRESS IS NULL) THEN 1 ELSE 0 END AS IF_MISSING_CONTACT
  ,CASE WHEN X1.CRM_ACCOUNT_ACTIVE_FLAG <= 0 THEN 1 ELSE 0 END AS IF_ACCOUNT_ACTIVE_FLAG
  ,CASE WHEN X2.MARKETABLE_CARDS_FLAG != 'Y' OR X2.DNS_CLVLE_DIGITAL_FLAG != 'I' THEN 1 ELSE 0 END AS IF_NOT_MARKETABLE_FLAG
  ,CASE WHEN (X2.ACMA_OPTIN = 'I' AND X2.SPAMHAUS_OPTIN = 'I') then 1 else 0 end as IF_ACMA_SPAMHAUS_ELIG
  FROM 
"PD_CUSTOMER_ANALYTICS"."CUSTOMER_ANALYTICS"."TBL_DM_ACCT_DETAILS" X1 
INNER JOIN "PD_CUSTOMER_ANALYTICS"."CUSTOMER_ANALYTICS"."TBL_DM_ACCT_ELIGIBILITY" X2
ON X1.CUST_ACCT_APPL_ID = X2.CUST_ACCT_APPL_ID 
LEFT JOIN "PD_CUSTOMER_ANALYTICS"."CUSTOMER_ANALYTICS"."TBL_DM_ACCT_CARD" X3
ON X1.CUST_ACCT_APPL_ID = X3.CUST_ACCT_APPL_ID 
WHERE X1.CRM_PRODUCT = '28DEGMC';

        
```

```{r}

DEGREES28_MKT_BASE %>% dplyr::count(IF_ACMA_SPAMHAUS_ELIG,ACMA_OPTIN,SPAMHAUS_OPTIN)

DEGREES28_MKT_BASE %>% dplyr::count(IF_NOT_MARKETABLE_FLAG,MARKETABLE_CARDS_FLAG,DNS_CLVLE_DIGITAL_FLAG)

```



```{r}
DEG28MC_waterfall <- DEGREES28_MKT_BASE %>% 
  mutate(DROPOUT_FLAG = case_when(
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_MISSING_CONTACT == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & OTB_LESSTHAN_300 == 0) ~ 'Total Passed Wash',
     IF_ACCOUNT_ACTIVE_FLAG == 1  ~ '1.ACCT-NOT-ACTIVE-EXCL',
    (IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_NOT_MARKETABLE_FLAG == 1) ~ '2.NON-MARKETABLE-AND-DNS-EXCL',
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_MISSING_CONTACT == 1 ) ~ '3.MISSING-CONTACT-EXCL',
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_MISSING_CONTACT == 0 & OTB_LESSTHAN_300 == 1 ) ~ '4.OTB-LESSTHAN-300-EXCL'
  ))

DEG28MC_waterfall %>% dplyr::count(DROPOUT_FLAG)

DEG28_t <- DEG28MC_waterfall %>%  group_by(DROPOUT_FLAG) %>% dplyr::summarise(T_NUM = n())
DEG28_t1 <- as.data.frame(DEG28_t)

waterfall(DEG28_t, calc_total = TRUE, total_axis_text = "AU Cards-Total",total_rect_color = "goldenrod1", total_rect_text_color = "black" )+coord_flip()+
  labs(title = "Waterfall Report for 28DEGMC ", 
       subtitle = "Total MARKETABLE", 
       x = "",
       y = "")+theme_minimal()

```

#### 28DEGMC ACCOUNTS MARKETABLE BASE

```{r}

DEGREES28_MKT_BASE1 <-DEGREES28_MKT_BASE %>% 
  filter(IF_NOT_MARKETABLE_FLAG == 0 & IF_MISSING_CONTACT == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & OTB_LESSTHAN_300 == 0)

count(DEGREES28_MKT_BASE1$CRM_PRODUCT)

range(DEGREES28_MKT_BASE1$CRM_OTB_AMT)

DEGREES28_MKT_BASE1 %>%  dplyr::count(IF_ACMA_SPAMHAUS_ELIG,ACMA_OPTIN,SPAMHAUS_OPTIN)



# CHECKING IF ANY DUPLICATES 

DEGREES28_MKT_BASE1 %>% get_dupes(CUST_ACCT_APPL_ID) %>% dplyr::summarize(n=n())


```


#### AVG INTERNATIONAL QUATERLY SPEND IN PAST YEAR 

```{sql connection=myconn, output.var = "DEGMC28_X1_TXN_CUBE"}

set (train_x1_startdate, train_x1_enddate) = (to_date('2022-04-01'), to_date('2023-03-30'));

```


```{sql connection=myconn, output.var = "DEGMC28_X1_TXN_AGGREGATION"}


SELECT 
CUST_ACCT_APPL_ID
,OVERALL_L12M_AVG_TXN_AMT
,I_L12M_AVG_TXN_AMT
,ROUND((I_Q2_AVG_TXN_AMT+I_Q3_AVG_TXN_AMT+I_Q4_AVG_TXN_AMT+I_Q1_AVG_TXN_AMT)/4,2) AS INTL_AVG_Q_AMT
FROM(
SELECT 
CUST_ACCT_APPL_ID
// now overall 28 degrees as a card DOMESTIC + INTERANATIONAL 
,SUM(TXN_AMT) AS OVERALL_TXN_AMT_L12M
,SUM(TXN_CNT) AS OVERALL_TXN_CNT_L12M
,COUNT(DISTINCT TRAN_YEAR_MTH) AS OVERALL_TXN_CNT_MNTH_L12M
,round((case when OVERALL_TXN_AMT_L12M = 0 
                  then 0 
                  else OVERALL_TXN_AMT_L12M/OVERALL_TXN_CNT_MNTH_L12M end),2) AS OVERALL_L12M_AVG_TXN_AMT
// International txns ONLY  
// L12M 
,SUM(case when CRM_INTL_FLAG = 'International' then TXN_AMT else 0 END ) AS I_TXN_AMT_L12M
,SUM(case when CRM_INTL_FLAG = 'International' then TXN_CNT ELSE 0 END) AS I_TXN_CNT_L12M
,COUNT(DISTINCT case when CRM_INTL_FLAG = 'International' THEN TRAN_YEAR_MTH  END) AS I_TXN_CNT_MNTH_L12M
,round((case when I_TXN_AMT_L12M = 0 
                  then 0 
                  else I_TXN_AMT_L12M/I_TXN_CNT_MNTH_L12M end),2) AS I_L12M_AVG_TXN_AMT
// FOR Q2 202204- 202206
,SUM(CASE WHEN CRM_INTL_FLAG = 'International' AND Q2_FLAG = 1 THEN TXN_AMT ELSE 0 END) AS I_TXN_AMT_Q2
,SUM(CASE WHEN CRM_INTL_FLAG = 'International' AND Q2_FLAG = 1 THEN TXN_CNT ELSE 0 END) AS I_TXN_CNT_Q2
,COUNT(DISTINCT CASE WHEN CRM_INTL_FLAG = 'International' AND Q2_FLAG = 1 THEN TRAN_YEAR_MTH END ) AS I_TXN_CNT_MNTH_Q2
,round((case when I_TXN_AMT_Q2 = 0 
                  then 0 
                  else I_TXN_AMT_Q2/I_TXN_CNT_MNTH_Q2 end),2) AS I_Q2_AVG_TXN_AMT
// FOR Q3 202207-202209
,SUM(CASE WHEN CRM_INTL_FLAG = 'International' AND Q3_FLAG = 1 THEN TXN_AMT ELSE 0 END) AS I_TXN_AMT_Q3
,SUM(CASE WHEN CRM_INTL_FLAG = 'International' AND Q3_FLAG = 1 THEN TXN_CNT ELSE 0 END) AS I_TXN_CNT_Q3
,COUNT(DISTINCT CASE WHEN CRM_INTL_FLAG = 'International' AND Q3_FLAG = 1 THEN TRAN_YEAR_MTH END ) AS I_TXN_CNT_MNTH_Q3
,round((case when I_TXN_AMT_Q3 = 0 
                  then 0 
                  else I_TXN_AMT_Q3/I_TXN_CNT_MNTH_Q3 end),2) AS I_Q3_AVG_TXN_AMT
// FOR Q4 202210- 202212
,SUM(CASE WHEN CRM_INTL_FLAG = 'International' AND Q4_FLAG = 1 THEN TXN_AMT ELSE 0 END) AS I_TXN_AMT_Q4
,SUM(CASE WHEN CRM_INTL_FLAG = 'International' AND Q4_FLAG = 1 THEN TXN_CNT ELSE 0 END) AS I_TXN_CNT_Q4
,COUNT(DISTINCT CASE WHEN CRM_INTL_FLAG = 'International' AND Q4_FLAG = 1 THEN TRAN_YEAR_MTH  END ) AS I_TXN_CNT_MNTH_Q4
,round((case when I_TXN_AMT_Q4 = 0 
                  then 0 
                  else I_TXN_AMT_Q4/I_TXN_CNT_MNTH_Q4 end),2) AS I_Q4_AVG_TXN_AMT
// FOR Q1 202301- 202303
,SUM(CASE WHEN CRM_INTL_FLAG = 'International' AND Q1_FLAG = 1 THEN TXN_AMT ELSE 0 END) AS I_TXN_AMT_Q1
,SUM(CASE WHEN CRM_INTL_FLAG = 'International' AND Q1_FLAG = 1 THEN TXN_CNT ELSE 0 END) AS I_TXN_CNT_Q1
,COUNT(DISTINCT CASE WHEN CRM_INTL_FLAG = 'International' AND Q1_FLAG = 1 THEN TRAN_YEAR_MTH  END ) AS I_TXN_CNT_MNTH_Q1
,round((case when I_TXN_AMT_Q1 = 0 
                  then 0 
                  else I_TXN_AMT_Q1/I_TXN_CNT_MNTH_Q1 end),2) AS I_Q1_AVG_TXN_AMT
from (
SELECT CUST_ACCT_APPL_ID
,CRM_TRAN_TYPE
,TRAN_YEAR_MTH
,CRM_INTL_FLAG
,MCC_GROUP
,IF_INTL_SPEND_ONLINE
,IF_INTL_SPEND_OTHER
,MOBILEWALLET_FLAG
,STARTDATE
,ENDDATE
,CASE WHEN TRAN_YEAR_MTH between '202204' and '202206' THEN 1 ELSE 0 END AS Q2_FLAG
,CASE WHEN TRAN_YEAR_MTH between '202207' and '202209' THEN 1 ELSE 0 END AS Q3_FLAG
,CASE WHEN TRAN_YEAR_MTH between '202210' and '202212' THEN 1 ELSE 0 END AS Q4_FLAG
,CASE WHEN TRAN_YEAR_MTH between '202301' and '202303' THEN 1 ELSE 0 END AS Q1_FLAG
 -- measurement:
		,sum(crm_amt_net) as TXN_AMT
		,count(1) as TXN_CNT
FROM ( select
        CUST_ACCT_APPL_ID
	    ,TRANDATE
        -- dimension:
        ,crm_tran_type
		,TO_CHAR(TRANDATE,'YYYYMM') AS TRAN_YEAR_MTH
        ,months_between($train_x1_enddate,TRANDATE) as MTHS_BTW_TXN_TODAY
		,datediff('day',$train_x1_enddate, TRANDATE) as DAYS_BTW_TXN_TODAY
		,ifnull(mcc_group,'UNKNOWN') as MCC_GROUP
        ,ifnull(CRM_MERCHANT,crm_tran_type) as CRM_MERCHANT
        ,case when CRM_INTL_FLAG =1 then 'International'
              when CRM_INTL_FLAG =0 then 'Domestic'
              else 'Unknown' end as CRM_INTL_FLAG
        ,crm_pos_entry
        ,case when crm_pos_entry = 'CARDNOTPRESENT_ONLINE' then 'Y' 
              when crm_pos_entry is null then 'UNKNOWN'
              else crm_pos_entry end as IF_ONLINE_SPEND
        ,case when crm_pos_entry = 'CARDNOTPRESENT_ONLINE' and CRM_INTL_FLAG = 1 then 'Y'
              when crm_pos_entry is null or CRM_INTL_FLAG is null then 'Unknown'
              else 'N' end as IF_INTL_SPEND_ONLINE
        ,CASE WHEN crm_pos_entry not in ('CARDNOTPRESENT_ONLINE') and CRM_INTL_FLAG = 1 then 'Y'
            when crm_pos_entry is null or CRM_INTL_FLAG is null then 'Unknown'
              else 'N' end as IF_INTL_SPEND_OTHER
        ,case when CRM_MOBILEWALLET_TYPE is null then 0 else 1 end as MOBILEWALLET_FLAG
        -- measurement:
		,crm_amt_net 
        //,case when (TRANDATE between $train_x_startdate and $train_x_enddate) then 'X' else 'Y' end as XY_TRANS_PERIOD
        ,case when (TRANDATE between $train_x1_startdate and $train_x1_enddate) then '2022-04-01'  end as STARTDATE
        ,case when (TRANDATE between $train_x1_startdate and $train_x1_enddate) then '2023-03-31' end as ENDDATE 
        
        //,row_number() over (partition by acct.cust_acct_appl_id, trans.crm_tran_type order by trans.TRANDATE desc) last_trans_by_type_cnt
		from "PD_CUSTOMER_ANALYTICS"."CONFORMED"."TBL_VP2_TXN_TRN"
		where crm_amt_net > 0 and crm_tran_type in ('SCH') and orgnbr = 330
        and ((TRANDATE between $train_x1_startdate and $train_x1_enddate))
)
GROUP BY 1,2,3,4,5,6,7,8,9,10,11,12,13,14
)
GROUP BY 1
)
;

```

#### GET THE PREDICTION TABLE 

```{sql connection=myconn, output.var = "DEGMC28_PREDICTION_X"}

SELECT *
FROM DATAIKU_AUTOMATION.CUSTOMER_ANALYTICS.NBO_28DEGMC_DEGMC28_PREDICTION


```

#### Join account table, txn table & predition table 

```{r}

T_28DEGMC_TABLE <- sqldf("select ACCT.CUST_ACCT_APPL_ID
  ,ACCT.CRM_PRODUCT
  ,ACCT.CRM_ACCOUNT_ACTIVE_FLAG
  ,ACCT.CREDITLIMIT
  ,ACCT.CRM_OTB_AMT
  ,ACCT.MARKETABLE_CARDS_FLAG
  ,ACCT.DNS_CLVLE_DIGITAL_FLAG 
  ,ACCT.ACMA_OPTIN 
  ,ACCT.SPAMHAUS_OPTIN 
  ,ACCT.IF_ACMA_SPAMHAUS_ELIG
  ,TXN.INTL_AVG_Q_AMT 
  ,PRED.PREDICTION_MORE_500MORE
  ,PRED.PREDICTION_MORE_500LESS
  ,PRED.PREDICTION_LESS
  ,PRED.PREDICTION_INACTIVE 
  ,CASE WHEN TXN.INTL_AVG_Q_AMT >=2000 OR PRED.PROBA_1_MORE_500MORE >= 0.80 THEN '1.SCH_MORE_OVER_$500'
        WHEN TXN.INTL_AVG_Q_AMT > 1001 AND TXN.INTL_AVG_Q_AMT < 2000 OR PRED.PROBA_1_MORE_500LESS >= 0.80 THEN '2.SCH_MORE_UNDER_$500'
        WHEN TXN.INTL_AVG_Q_AMT > 0 AND TXN.INTL_AVG_Q_AMT < 1000  OR PRED.PROBA_1_LESS >= 0.70 THEN '3.SCH_LESS'
        WHEN (TXN.INTL_AVG_Q_AMT IS null  OR TXN.INTL_AVG_Q_AMT = 0) OR PROBA_1_INACTIVE >= 0.70 THEN '4.SCH_INACTIVE'
           END AS SUBSEG
   from DEGREES28_MKT_BASE1 ACCT
   LEFT JOIN DEGMC28_X1_TXN_AGGREGATION TXN
   ON ACCT.CUST_ACCT_APPL_ID = TXN.CUST_ACCT_APPL_ID 
   LEFT JOIN DEGMC28_PREDICTION_X PRED
   ON ACCT.CUST_ACCT_APPL_ID = PRED.CUST_ACCT_APPL_ID 
  ")

```



```{r}

SUBSEG_CHECK_T <- T_28DEGMC_TABLE %>% 
  select(INTL_AVG_Q_AMT, SUBSEG, PREDICTION_MORE_500MORE,PREDICTION_MORE_500LESS,PREDICTION_LESS,PREDICTION_INACTIVE)

T_28DEGMC_TABLE %>% dplyr::count(SUBSEG)

T_28DEGMC_TABLE %>% dplyr::count(CRM_PRODUCT)

```


#### TOTAL COUNT WITH CRM_OTB_AMT >= $1000 | COUNT OF SUBSEGMENTS 
```{r}

T_28DEGMC_TABLE %>% 
  dplyr::count(CRM_PRODUCT)

## CRM_OTB_AMT >= 1000
T_28DEGMC_TABLE %>% 
  filter (CRM_OTB_AMT < 1000) %>%
  dplyr::count(CRM_PRODUCT)
  
## COUNT OF SUBSEG 


T_28DEGMC_TABLE %>% 
  dplyr::count(SUBSEG)

```

#### CALCULATING THE $ THRESHOLD AND THE OFFER AMOUNT 

```{r}

T_28DEGMC_TABLE <- T_28DEGMC_TABLE %>%
  mutate(INTL_AVG_Q_AMT = if_else(is.na(INTL_AVG_Q_AMT),0,INTL_AVG_Q_AMT))

```


```{r}

T_28DEGMC_TABLE_1 <- T_28DEGMC_TABLE %>%
  filter (!is.na(SUBSEG)) %>%
  mutate(SEG = "Scheme",
         CRM_PRODUCT_VARIANT = "",
         CUSTOMER_ID = CUST_ACCT_APPL_ID,
         THRESHOLD_CHECK = case_when(
           SUBSEG == "1.SCH_MORE_OVER_$500" ~ INTL_AVG_Q_AMT+2000,
           SUBSEG == "2.SCH_MORE_UNDER_$500" ~ INTL_AVG_Q_AMT+1500,
           SUBSEG == "3.SCH_LESS" ~ INTL_AVG_Q_AMT+1200,
           SUBSEG == "4.SCH_INACTIVE" ~ 1000
         ),
          THRESHOLD = case_when(
           SUBSEG == "1.SCH_MORE_OVER_$500" ~ (round(round_any(INTL_AVG_Q_AMT+2000,100,f=ceiling))),
           SUBSEG == "2.SCH_MORE_UNDER_$500" ~ (round(round_any(INTL_AVG_Q_AMT+1500,100,f=ceiling))),
           SUBSEG == "3.SCH_LESS" ~ (round(round_any(INTL_AVG_Q_AMT+1200,100,f=ceiling))) ,
           SUBSEG == "4.SCH_INACTIVE" ~ (round(1000))
         ),
         OFFER = case_when(
           SUBSEG == "1.SCH_MORE_OVER_$500" ~ "150",
           SUBSEG == "2.SCH_MORE_UNDER_$500" ~ "100",
           SUBSEG == "3.SCH_LESS" ~ "50",
           SUBSEG == "4.SCH_INACTIVE" ~ "50"
         )
  )

range(T_28DEGMC_TABLE_1$CRM_OTB_AMT)

```

#### 

```{r}

COUNT_OTB_CL_WASH <- T_28DEGMC_TABLE_1 %>% 
  mutate( CREDITLIMIT_FLAG = case_when(
        THRESHOLD > CREDITLIMIT ~ "threshold > Cl",
        THRESHOLD > 6000 ~ "Spend threshold > 6000"
  ))

check_table <- table(COUNT_OTB_CL_WASH$SUBSEG, COUNT_OTB_CL_WASH$CREDITLIMIT_FLAG)
ftable(check_table)


T_28DEGMC_TABLE_2 <- T_28DEGMC_TABLE_1 %>%
   mutate(THRESHOLD = case_when(
        THRESHOLD <= 6000 ~ THRESHOLD, 
        THRESHOLD > 6000 ~ 6000,
        THRESHOLD > CREDITLIMIT ~ CREDITLIMIT,
  ),
        threshold_range = case_when (
          THRESHOLD <= 1000 ~ "$1000",
          THRESHOLD>1000 & THRESHOLD < 1200 ~ "$1001-$1199",
          THRESHOLD>=1200 & THRESHOLD < 1500 ~ "$1200-$1499",
          THRESHOLD>=1500 & THRESHOLD <= 1999 ~ "$1500-$2000",
          THRESHOLD>=2000 & THRESHOLD <= 3000 ~ "$2001-$3000",
          THRESHOLD>3000 & THRESHOLD <= 4000 ~ "$3001-$4000",
          THRESHOLD>4000 & THRESHOLD <= 6000 ~ "$4001-$6000",
          THRESHOLD > 6000 ~ "$6000+"
        ))


```


```{r}
##str(T_28DEGMC_TABLE_2)

#CHECK THE RANGE OF THE SPEND THRESHOLD

count(T_28DEGMC_TABLE_2$CRM_PRODUCT)

# RANGE OF THE THRESHOLD 

range(T_28DEGMC_TABLE_2$CRM_OTB_AMT)

range(T_28DEGMC_TABLE_2$THRESHOLD)

## FREQ TABLE FOR THE SPEND THRESHOLD RANGE 
check_table_2 <- table(T_28DEGMC_TABLE_2$SUBSEG, T_28DEGMC_TABLE_2$threshold_range, T_28DEGMC_TABLE_2$OFFER)
ftable(check_table_2)



ggplot(T_28DEGMC_TABLE_2, aes(x=SUBSEG, fill = threshold_range))+
  geom_bar(position = "fill")+
  ylab("propotion")+coord_flip()+
     scale_fill_hue(c=45, l=80)+
          theme_bw()
```


#### FREQUENCIES OF TOTAL PASS WASH

```{r}

count(T_28DEGMC_TABLE_2$SUBSEG)
count(T_28DEGMC_TABLE_2$CRM_PRODUCT)

# MARKETABLE FLAG IS 'Y' & DNS_CLVLE_DIGITAL_FLAG IS 'I'

check_table_3 <- table(T_28DEGMC_TABLE_2$MARKETABLE_CARDS_FLAG, T_28DEGMC_TABLE_2$DNS_CLVLE_DIGITAL_FLAG)
ftable(check_table_3)

# 

check_table_4 <- table(T_28DEGMC_TABLE_2$SUBSEG, T_28DEGMC_TABLE_2$IF_ACMA_SPAMHAUS_ELIG)
ftable(check_table_4)

X <- table(T_28DEGMC_TABLE_2$IF_ACMA_SPAMHAUS_ELIG,T_28DEGMC_TABLE_2$ACMA_OPTIN,T_28DEGMC_TABLE_2$SPAMHAUS_OPTIN)
ftable(X)
##view(check_table_4)

PLOTy <- T_28DEGMC_TABLE_2 %>%
          group_by(ACMA_OPTIN, SPAMHAUS_OPTIN)%>%
           dplyr::summarise(num = n(),
                            NUM_LEADS = comma(n()))


ggplot(PLOTy, aes(x=ACMA_OPTIN, y= num,fill = SPAMHAUS_OPTIN))+
  geom_bar(stat =  "identity")+
     scale_fill_hue(c=45, l=80)+
  geom_text(aes(label = NUM_LEADS),size = 2.5,position=position_dodge(width=0.9), vjust=-0.25)+
          theme_bw()
```

#### BUILDING THE CAMPAIGN DATA CONTROL GROUP AND OFFER_ACTIVATED_FLAG & SPEND_QUALIFIED_FLAG 

```{r}

PET_CA_857_TRAVEL_Q <- sqldf(
  "
  SELECT CUSTOMER_ID
  ,CRM_PRODUCT
  ,CRM_PRODUCT_VARIANT
  ,SEG
  ,SUBSEG
  ,THRESHOLD
  ,OFFER
  ,'SG_CA_857_28DEGMC_TRAVELQ' as CAMPAIGN_ID
  ,	'2023-07-05' as  EXPIRY_DATE
  , '2023-07-04' as CAMPAIGN_START_DATE
  , '2023-09-30' as CAMPAIGN_END_DATE
  ,case when row_number() over (partition by SUBSEG order by random()) <=
                  0.4 * count(*) over (partition by SUBSEG) 
             then 'Y'
             else 'N'
             end as CONTROL_GROUP 
  ,'' as OFFER_ACTIVATED_FLAG
  ,''AS SPEND_QUALIFIED_FLAG
  FROM T_28DEGMC_TABLE_2
  "
)

dim(T_28DEGMC_TABLE_2)

dim(PET_CA_857_TRAVEL_Q)

```

#### CHECK CONTROL_GROUP & SUBSEGS 

```{r}


check_table_5 <- table(PET_CA_857_TRAVEL_Q$SUBSEG, PET_CA_857_TRAVEL_Q$CONTROL_GROUP)
ftable(check_table_5)

count(PET_CA_857_TRAVEL_Q$SUBSEG)
count(PET_CA_857_TRAVEL_Q$CRM_PRODUCT)


check_table_6 <- table(PET_CA_857_TRAVEL_Q$OFFER_ACTIVATED_FLAG, PET_CA_857_TRAVEL_Q$SPEND_QUALIFIED_FLAG)
ftable(check_table_6)

## plots for the counts 

PLOTx <- PET_CA_857_TRAVEL_Q %>%
          group_by(CONTROL_GROUP)%>%
           dplyr::summarise(num = n(),
                            NUM_LEADS = comma(n()))

ggplot(PLOTx,aes(x= CONTROL_GROUP,y = num , fill = CONTROL_GROUP))+
            geom_bar(stat = "identity",position = "dodge")+
        scale_fill_brewer(palette="Spectral")+
          theme_bw()+
  geom_text(aes(label = NUM_LEADS),size = 2.5,position=position_dodge(width=0.9), vjust=-0.25)+
  labs(
    x = "Segments",
    y = "",
    fill = "CONTROL_GROUP"
        )


PLOT1 <- PET_CA_857_TRAVEL_Q %>%
          group_by(SUBSEG,CONTROL_GROUP)%>%
           dplyr::summarise(num = n(),
                            NUM_LEADS = comma(n()))

ggplot(PLOT1,aes(x= SUBSEG,y = num , fill = CONTROL_GROUP))+
            geom_bar(stat = "identity",position = "dodge")+
         scale_fill_brewer(palette="Spectral")+
          theme_bw()+coord_flip()+
  geom_text(aes(label = NUM_LEADS),size = 2.5,position=position_dodge(width=0.9), vjust=-0.25)+
  labs(
    x = "Segments",
    y = "",
    fill = "CONTROL_GROUP"
        )

PLOT2 <- PET_CA_857_TRAVEL_Q %>%
            filter(CONTROL_GROUP == 'N') %>%
          group_by(SUBSEG,OFFER)%>%
           dplyr::summarise(num = n(),
                            NUM_LEADS = comma(n()))

ggplot(PLOT2,aes(x= SUBSEG,y = num , fill = OFFER))+
            geom_bar(stat = "identity",position = "dodge")+
         scale_fill_brewer(palette="Spectral")+
          theme_bw()+coord_flip()+
  geom_text(aes(label = NUM_LEADS),size = 2.5,position=position_dodge(width=0.9), vjust=-0.25)+
  labs(
    x = "Segments",
    y = "",
    fill = "OFFER"
        )


```

#### TEST SEEDS TO GENERATE FOR OFFER_ACTIVATED_FLAG & SPEND_QUALIFIED_FLAG

```{r}

SEED_1 <- PET_CA_857_TRAVEL_Q %>%
  arrange(desc(THRESHOLD)) %>%
  group_by(SUBSEG, CONTROL_GROUP) %>%
  slice(1) %>%
  mutate(
    OFFER_ACTIVATED_FLAG = case_when(
      CONTROL_GROUP == 'Y' ~ 'N',
      CONTROL_GROUP == 'N' ~ 'Y',
  
    ),
    SPEND_QUALIFIED_FLAG = case_when(
      CONTROL_GROUP == 'Y' ~ 'N',
      CONTROL_GROUP == 'N' ~ 'N',
    )
  )%>%
  ungroup()

shuffled_data= PET_CA_857_TRAVEL_Q[sample(1:nrow(PET_CA_857_TRAVEL_Q)), ]

SEED_2 <- shuffled_data %>%
  filter(CONTROL_GROUP == 'N') %>%
  group_by(SUBSEG) %>%
  slice(2) %>%
  mutate(
    OFFER_ACTIVATED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'Y',
    ),
    SPEND_QUALIFIED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'Y',
    )
  )%>%
  ungroup()

shuffled_data1 = PET_CA_857_TRAVEL_Q[sample(1:nrow(PET_CA_857_TRAVEL_Q)), ]


SEED_3 <- shuffled_data1 %>%
  filter(CONTROL_GROUP == 'N') %>%
  group_by(SUBSEG) %>%
  slice(1) %>%
  mutate(
    OFFER_ACTIVATED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'N',
    ),
    SPEND_QUALIFIED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'Y',
    )
  )%>%
  ungroup()

shuffled_data2 = PET_CA_857_TRAVEL_Q[sample(1:nrow(PET_CA_857_TRAVEL_Q)), ]

SEED_4 <- shuffled_data2 %>%
  filter(CONTROL_GROUP == 'N') %>%
  group_by(SUBSEG) %>%
  slice(1) %>%
  mutate(
    OFFER_ACTIVATED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'N',
    ),
    SPEND_QUALIFIED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'N',
    )
  )%>%
  ungroup()

SEEDS_TEST_DATA <- bind_rows(SEED_1,SEED_2,SEED_3,SEED_4)


## TABLE 6

check_table_6 <- table(SEEDS_TEST_DATA$CONTROL_GROUP, SEEDS_TEST_DATA$OFFER_ACTIVATED_FLAG,
                       SEEDS_TEST_DATA$SPEND_QUALIFIED_FLAG)
ftable(check_table_6)


str(SEEDS_TEST_DATA)

```



```{r}

## for seeds 

PET_CA_857_SEEDS<- SEEDS_TEST_DATA %>% 
   dplyr::mutate(CUSTOMER_ID = paste("TEST", CRM_PRODUCT,"C360",row_number(),sep = "_") )
  

```

#### CREATING THE PRODUCTION DATA 

```{r}
PET_SG_CA857_28DEGMC_TRAVEL_Q <- bind_rows(PET_CA_857_TRAVEL_Q,PET_CA_857_SEEDS)

str(PET_SG_CA857_28DEGMC_TRAVEL_Q)

PET_SG_CA857_28DEGMC_TRAVEL_Q %>% dplyr::count(CRM_PRODUCT)

PET_SG_CA857_28DEGMC_TRAVEL_Q %>% dplyr::count(CRM_PRODUCT,CONTROL_GROUP)

PET_SG_CA857_28DEGMC_TRAVEL_Q %>% dplyr::count(CRM_PRODUCT,CONTROL_GROUP,SUBSEG)

range(PET_SG_CA857_28DEGMC_TRAVEL_Q$THRESHOLD)
# checking duplicates

PET_SG_CA857_28DEGMC_TRAVEL_Q %>% get_dupes(CUSTOMER_ID) %>% dplyr::summarize(n=n())


```

#### Expected final treatment group after SPAMHAUS FILTERS 

```{r}

  
SPAMHAUS_CHECK <- sqldf("
SELECT A.* 
,X.ACMA_OPTIN
,X.SPAMHAUS_OPTIN
,X.IF_ACMA_SPAMHAUS_ELIG
FROM PET_SG_CA857_28DEGMC_TRAVEL_Q A 
LEFT JOIN T_28DEGMC_TABLE_2 X
ON A.CUSTOMER_ID = X.CUSTOMER_ID
WHERE A.CONTROL_GROUP = 'N'
                        ")


PLOT_SPAMHAUS <- SPAMHAUS_CHECK %>%
          group_by(ACMA_OPTIN, SPAMHAUS_OPTIN)%>%
           dplyr::summarise(num = n(),
                            NUM_LEADS = comma(n()))


ggplot(PLOT_SPAMHAUS, aes(x=ACMA_OPTIN, y= num,fill = SPAMHAUS_OPTIN))+
  geom_bar(stat =  "identity")+
     scale_fill_hue(c=45, l=80)+
  geom_text(aes(label = NUM_LEADS),size = 3,position=position_dodge(width=0.9), vjust=-0.25)+
          theme_bw()
```





#### Transfering the PET back to snowflake


```{r}

table_id <- Id(database = Sys.getenv('CUSTOMER_ANALYTICS_WORKSPACE_DB'), schema = "CAMPAIGN_AUDIENCE", table = "PET_SG_CA857_28DEGMC_TRAVEL_Q")

dbWriteTable(myconn, table_id,PET_SG_CA857_28DEGMC_TRAVEL_Q, overwrite = TRUE)

```