---
title: "Nov23_GOLDENQ"
author: "Kuljeet"
date: "9/28/2023"
output: html_document
---

```{r, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DBI)
library(plyr)
library(dplyr)
library(dbplyr)
library(odbc)
library(DT)
library(tidyverse)
library(data.table)
library(waterfalls)
library(ggplot2)
library(janitor)
library(scales)
library (sqldf)
library(ggthemes)
library(rmarkdown)

```

```{r}

readRenviron(".renviron") 


database <- "PD_CUSTOMER_ANALYTICS"
myconn <- DBI::dbConnect(odbc::odbc(), "SNOWFLAKEC360", 
                         database = "PD_CUSTOMER_ANALYTICS", 
                         uid = if(Sys.getenv('SNOWFLAKE_UID') != "") Sys.getenv('SNOWFLAKE_UID') else NULL,
                         token = if(Sys.getenv('SNOWFLAKE_C360_TOKEN') != "") Sys.getenv('SNOWFLAKE_C360_TOKEN') else NULL)

```

#### Product: GOMC; GEMV; GEMVNZ 

```{sql connection=myconn, output.var = "ACTUAL_BASE"}

SELECT 
  X1.CUST_ACCT_APPL_ID
  ,X1.CRM_PRODUCT
  ,X1.CRM_PRODUCT_VARIANT
  ,X1.CRM_ACCOUNT_ACTIVE_FLAG
  ,X1.FIRST_NAME
  ,X1.EMAILADDRESS
  ,X3.STATUSCURR
  ,X1.GENDER
  ,X3.CRM_MOB
  ,X3.top_dealer_name
  ,ROUND(X1.CREDITLIMIT_AMT) AS CREDITLIMIT
  ,X1.CURR_BAL_AMT
  ,X3.CRM_OTB_AMT
  ,X2.MARKETABLE_CARDS_FLAG
  ,X2.DNS_CLVLE_DIGITAL_FLAG 
  ,X2.ACMA_OPTIN 
  ,X2.SPAMHAUS_OPTIN 
  ,CASE WHEN ((X1.CREDITLIMIT_AMT - X1.CURR_BAL_AMT <= 300)) THEN 1 ELSE 0 END AS OTB_LESSTHAN_300
  ,CASE WHEN (X1.FIRST_NAME IS NULL or X1.EMAILADDRESS IS NULL) THEN 1 ELSE 0 END AS IF_MISSING_CONTACT
  ,CASE WHEN X1.CRM_ACCOUNT_ACTIVE_FLAG <= 0 THEN 1 ELSE 0 END AS IF_ACCOUNT_ACTIVE_FLAG
  ,CASE WHEN X2.MARKETABLE_CARDS_FLAG != 'Y' OR X2.DNS_CLVLE_DIGITAL_FLAG != 'I' THEN 1 ELSE 0 END AS IF_NOT_MARKETABLE_FLAG
  ,CASE WHEN (X2.SPAMHAUS_OPTIN = 'I' AND X2.ACMA_OPTIN IS NULL ) THEN 1 else 0 end as IF_SPAMHAUS_INELIG
  FROM 
"PD_CUSTOMER_ANALYTICS"."CUSTOMER_ANALYTICS"."TBL_DM_ACCT_DETAILS" X1 
INNER JOIN "PD_CUSTOMER_ANALYTICS"."CUSTOMER_ANALYTICS"."TBL_DM_ACCT_ELIGIBILITY" X2
ON X1.CUST_ACCT_APPL_ID = X2.CUST_ACCT_APPL_ID 
LEFT JOIN "PD_CUSTOMER_ANALYTICS"."CUSTOMER_ANALYTICS"."TBL_DM_ACCT_CARD" X3
ON X1.CUST_ACCT_APPL_ID = X3.CUST_ACCT_APPL_ID 
WHERE X1.CRM_PRODUCT IN ('GOMC','GEMV','GEMVNZ');

        
```

```{r count-check}


# ACTUAL_BASE %>% count(CRM_PRODUCT,IF_NOT_MARKETABLE_FLAG,IF_ACCOUNT_ACTIVE_FLAG,IF_SPAMHAUS_INELIG,IF_MISSING_CONTACT, OTB_LESSTHAN_300)

# ACTUAL_BASE %>% filter(CRM_PRODUCT =='GEMV' & IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG ==0) %>% count(IF_SPAMHAUS_INELIG,ACMA_OPTIN,SPAMHAUS_OPTIN)

# ACTUAL_BASE %>% filter(CRM_PRODUCT =='GOMC') %>% count(CRM_PRODUCT,IF_NOT_MARKETABLE_FLAG,IF_ACCOUNT_ACTIVE_FLAG,IF_SPAMHAUS_INELIG,IF_MISSING_CONTACT, OTB_LESSTHAN_300)

ACTUAL_BASE %>% dplyr::count(CRM_PRODUCT,CRM_PRODUCT_VARIANT)

```

### Waterfall report for GOMC

```{r waterfall-report}

## For GOMC

WATERFALL_GOMC <- ACTUAL_BASE %>% filter(CRM_PRODUCT == 'GOMC') %>%
  mutate(DROPOUT_FLAG = case_when(
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_SPAMHAUS_INELIG == 0 & IF_MISSING_CONTACT == 0 & OTB_LESSTHAN_300 == 0) ~ 'Total GOMC Passed Wash',
     IF_ACCOUNT_ACTIVE_FLAG == 1  ~ '1.ACCT-NOT-ACTIVE-EXCL',
    ( IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_NOT_MARKETABLE_FLAG == 1) ~ '2.NON-MARKETABLE-AND-DNS-EXCL',
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_MISSING_CONTACT == 1 ) ~ '3.MISSING-CONTACT-EXCL' ,
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_MISSING_CONTACT == 0 & IF_SPAMHAUS_INELIG == 1) ~ '4.SPAMHAUS-INELIGIBLE-EXCL' ,
     (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_SPAMHAUS_INELIG == 0 & IF_MISSING_CONTACT == 0 & OTB_LESSTHAN_300 == 1) ~ '5.OTB-LESSTHAN-300-EXCL'
  ))
 

WATERFALL_GOMC %>% dplyr::count(DROPOUT_FLAG)

GOMC <- WATERFALL_GOMC %>%  group_by(DROPOUT_FLAG) %>% dplyr::summarise(T_NUM = n())
GOMC_T1 <- as.data.frame(GOMC)

waterfall(GOMC_T1, calc_total = TRUE, total_axis_text = "GOMC-Total",total_rect_color = "orange", total_rect_text_color = "black" )+coord_flip()+
  labs(title = "Waterfall Report for GOMC ", 
       subtitle = "Total MARKETABLE FOR GOMC", 
       x = "",
       y = "")+theme_minimal()

```

### Waterfall report for GEMV

```{r waterfall-report-GEMV}

## For GEMV

WATERFALL_GEMV <- ACTUAL_BASE %>% filter(CRM_PRODUCT == 'GEMV') %>%
  mutate(DROPOUT_FLAG = case_when(
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_SPAMHAUS_INELIG == 0 & IF_MISSING_CONTACT == 0 & OTB_LESSTHAN_300 == 0) ~ 'Total GEMV Passed Wash',
     IF_ACCOUNT_ACTIVE_FLAG == 1  ~ '1.ACCT-NOT-ACTIVE-EXCL',
    ( IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_NOT_MARKETABLE_FLAG == 1) ~ '2.NON-MARKETABLE-AND-DNS-EXCL',
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_MISSING_CONTACT == 1 ) ~ '3.MISSING-CONTACT-EXCL' ,
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_MISSING_CONTACT == 0 & IF_SPAMHAUS_INELIG == 1) ~ '4.SPAMHAUS-INELIGIBLE-EXCL' ,
     (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_SPAMHAUS_INELIG == 0 & IF_MISSING_CONTACT == 0 & OTB_LESSTHAN_300 == 1) ~ '5.OTB-LESSTHAN-300-EXCL'
  ))
 

WATERFALL_GEMV %>% dplyr::count(DROPOUT_FLAG)

GEMV <- WATERFALL_GEMV %>%  group_by(DROPOUT_FLAG) %>% dplyr::summarise(T_NUM = n())
GEMV_T1 <- as.data.frame(GEMV)

waterfall(GEMV_T1, calc_total = TRUE, total_axis_text = "GEMV-Total",total_rect_color = "light green", total_rect_text_color = "black" )+coord_flip()+
  labs(title = "Waterfall Report for GEMV ", 
       subtitle = "Total MARKETABLE FOR GEMV", 
       x = "",
       y = "")+theme_minimal()

``` 


### Waterfall report for GEMVNZ

```{r waterfall-report-GEMVNZ}

## For GEMV

WATERFALL_GEMVNZ <- ACTUAL_BASE %>% filter(CRM_PRODUCT == 'GEMVNZ') %>%
  mutate(DROPOUT_FLAG = case_when(
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_SPAMHAUS_INELIG == 0 & IF_MISSING_CONTACT == 0 & OTB_LESSTHAN_300 == 0) ~ 'Total GEMVNZ Passed Wash',
     IF_ACCOUNT_ACTIVE_FLAG == 1  ~ '1.ACCT-NOT-ACTIVE-EXCL',
    ( IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_NOT_MARKETABLE_FLAG == 1) ~ '2.NON-MARKETABLE-AND-DNS-EXCL',
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_MISSING_CONTACT == 1 ) ~ '3.MISSING-CONTACT-EXCL' ,
    (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_MISSING_CONTACT == 0 & IF_SPAMHAUS_INELIG == 1) ~ '4.SPAMHAUS-INELIGIBLE-EXCL' ,
     (IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_SPAMHAUS_INELIG == 0 & IF_MISSING_CONTACT == 0 & OTB_LESSTHAN_300 == 1) ~ '5.OTB-LESSTHAN-300-EXCL'
  ))
 

WATERFALL_GEMVNZ %>% dplyr::count(DROPOUT_FLAG)

GEMVNZ <- WATERFALL_GEMVNZ %>%  group_by(DROPOUT_FLAG) %>% dplyr::summarise(T_NUM = n())
GEMVNZ_T1 <- as.data.frame(GEMVNZ)

waterfall(GEMVNZ_T1, calc_total = TRUE, total_axis_text = "GEMVNZ-Total",total_rect_color = "pink", total_rect_text_color = "black" )+coord_flip()+
  labs(title = "Waterfall Report for GEMVNZ ", 
       subtitle = "Total MARKETABLE FOR GEMVNZ", 
       x = "",
       y = "")+theme_minimal()

```

#### ALL ACCOUNTS MARKETABLE BASE

```{r}
MARKETABLE_BASE <- ACTUAL_BASE %>% 
filter(IF_NOT_MARKETABLE_FLAG == 0 & IF_ACCOUNT_ACTIVE_FLAG == 0 & IF_SPAMHAUS_INELIG == 0 & IF_MISSING_CONTACT == 0 & OTB_LESSTHAN_300 == 0)
```


```{r}

MARKETABLE_BASE %>% dplyr::count(CRM_PRODUCT)

# MARKETABLE_BASE %>% range(CRM_OTB_AMT)

MARKETABLE_BASE %>%  dplyr::count(IF_SPAMHAUS_INELIG,ACMA_OPTIN,SPAMHAUS_OPTIN)

# CHECKING GEMVNZ FOR HN AND NONHN 

MARKETABLE_BASE %>% filter(CRM_PRODUCT == 'GEMVNZ') %>%
  mutate(CHECKPOINT = if_else(
    TOP_DEALER_NAME %in% ('Harvey Norman') | TOP_DEALER_NAME %in% ('NZ Harvey Norman'), "HN","NONHN"
  ) ) %>%
 dplyr::count(CHECKPOINT)



# CHECKING IF ANY DUPLICATES 

MARKETABLE_BASE %>% get_dupes(CUST_ACCT_APPL_ID) %>% dplyr::summarize(n=n())


```

### Average monthly spend from last 6 months txns 

```{sql connection=myconn, output.var = "L6MDATES"}

set (train_x1_startdate, train_x1_enddate) = (to_date('2023-04-01'), to_date('2023-09-30'));

```

```{sql connection=myconn, output.var = "L6M_TXN"}

    select cust_acct_appl_id
    ,ORGNBR
,sum(crm_amt_net) as txn_l6m_amt
,count(1) as txn_cnt
,COUNT(DISTINCT TRAN_YEAR_MTH) AS TXN_CNT_MNTH_L6M
,round((case when txn_l6m_amt = 0 
                  then 0 
                  else txn_l6m_amt/TXN_CNT_MNTH_L6M end),2) AS L6M_AVG_TXN_AMT
from 
(
select
        CUST_ACCT_APPL_ID
        ,ORGNBR
	    ,TRANDATE
      ,crm_tran_type
		  ,TO_CHAR(TRANDATE,'YYYYMM') AS TRAN_YEAR_MTH
      ,months_between($train_x1_enddate,TRANDATE) as MTHS_BTW_TXN_TODAY
	    ,datediff('day',$train_x1_enddate, TRANDATE) as DAYS_BTW_TXN_TODAY
		  ,ifnull(mcc_group,'UNKNOWN') as MCC_GROUP
      ,ifnull(CRM_MERCHANT,crm_tran_type) as CRM_MERCHANT
      ,crm_pos_entry
		  ,crm_amt_net 
		from "PD_CUSTOMER_ANALYTICS"."CUSTOMER_ANALYTICS"."TBL_DM_TXN_CARD"
		where crm_amt_net > 0 and crm_tran_type in ('SCH') and orgnbr in (161,160,550,450) 
        and ((TRANDATE between $train_x1_startdate and $train_x1_enddate)
        ))
         GROUP BY 1,2

```

```{sql connection=myconn, output.var = "PREDICTION_TABLE"}

    SELECT
                CUST_ACCT_APPL_ID,
                CRM_PRODUCT,
                Y_SCH_NO,
                Y_SCH_MORE_UNDER_500,
                Y_SCH_MORE_OVER_500,
                Y_SCH_LESS
    FROM ML_MODELS.NEXT_BEST_OFFER.GEMV_PREDICTION
    WHERE
                YEAR_MONTH IN ('2022Nov') 
                   AND CRM_PRODUCT IN ('GEMV','GEMVNZ')            

    UNION 
       SELECT
                CUST_ACCT_APPL_ID,
                CRM_PRODUCT,
                Y_SCH_NO,
                Y_SCH_MORE_UNDER_500,
                Y_SCH_MORE_OVER_500,
                Y_SCH_LESS
    FROM ML_MODELS.NEXT_BEST_OFFER.GOMC_PREDICTION
    WHERE
                YEAR_MONTH IN ('2022Nov') 
                   AND CRM_PRODUCT IN ('GOMC')
    ;

```

### JOIN MARKETABLE BASE, PREDICTION SCORES & AVG L6M TXNS

```{r}

TOTAL_CAMPAIGN_BASE <- sqldf(
  "
  SELECT MKT.*
    ,TXN.txn_l6m_amt
    ,TXN.L6M_AVG_TXN_AMT
    ,PRED.Y_SCH_MORE_OVER_500
    ,PRED.Y_SCH_MORE_UNDER_500
    ,PRED.Y_SCH_LESS
    ,PRED.Y_SCH_NO
    ,case when row_number() over (partition by MKT.crm_product order by random()) <=
                  0.5 * count(*) over (partition by MKT.crm_product) 
             then 'SCH'
            WHEN MKT.CRM_PRODUCT = 'GOMC' THEN 'RP_GOMC_HN'
            WHEN MKT.CRM_PRODUCT = 'GEMV' THEN 'RP_GEMV_JBHI'
            WHEN MKT.CRM_PRODUCT = 'GEMVNZ' AND TOP_DEALER_NAME IN ('Harvey Norman','NZ Harvey Norman') THEN 'RP_GEMVNZ_HN'
            WHEN MKT.CRM_PRODUCT = 'GEMVNZ' AND TOP_DEALER_NAME NOT IN ('Harvey Norman','NZ Harvey Norman') OR TOP_DEALER_NAME IS NULL THEN 'RP_GEMVNZ_NONHN'
        end as SEG
    ,CASE WHEN TXN.L6M_AVG_TXN_AMT >=2000 OR PRED.Y_SCH_MORE_OVER_500 >= 0.85 THEN '1.SCH_MORE_OVER_$500'
        WHEN TXN.L6M_AVG_TXN_AMT > 1000 AND TXN.L6M_AVG_TXN_AMT< 2000 OR PRED.Y_SCH_MORE_UNDER_500 >= 0.80 THEN   '2.SCH_MORE_UNDER_$500'
        WHEN TXN.L6M_AVG_TXN_AMT > 0 AND TXN.L6M_AVG_TXN_AMT <= 1000  OR PRED.Y_SCH_LESS >= 0.80 THEN '3.SCH_LESS'
        WHEN (TXN.L6M_AVG_TXN_AMT IS null  OR TXN.L6M_AVG_TXN_AMT<= 0) OR PRED.Y_SCH_NO >= 0.70 THEN '4.SCH_INACTIVE'
        END AS SUBSEG
    FROM MARKETABLE_BASE MKT 
    LEFT JOIN L6M_TXN TXN 
    ON MKT.CUST_ACCT_APPL_ID = TXN.CUST_ACCT_APPL_ID
    LEFT JOIN PREDICTION_TABLE PRED
    ON MKT.CUST_ACCT_APPL_ID = PRED.CUST_ACCT_APPL_ID 
    ORDER BY PRED.Y_SCH_MORE_OVER_500 DESC NULLS LAST,
    PRED.Y_SCH_MORE_UNDER_500 DESC NULLS LAST,
    PRED.Y_SCH_LESS DESC NULLS LAST,
    PRED.Y_SCH_NO DESC NULLS LAST
    "
)
```

### ASSIGNING THE SEGMENTS & SUBSEGMENTS 

```{r}

TOTAL_CAMPAIGN_BASE %>% filter(CRM_PRODUCT == 'GEMVNZ') %>%
  mutate(CHECKPOINT = if_else(
    TOP_DEALER_NAME %in% ('Harvey Norman') | TOP_DEALER_NAME %in% ('NZ Harvey Norman'), "HN","NONHN"
  ) ) %>%
  dplyr::count(SEG,CHECKPOINT)

TOTAL_CAMPAIGN_BASE %>% filter(CRM_PRODUCT == 'GEMVNZ' & is.na(SEG)) %>% select(TOP_DEALER_NAME)
  

TOTAL_CAMPAIGN_BASE %>% dplyr::count(CRM_PRODUCT,SUBSEG)

TOTAL_CAMPAIGN_BASE %>% dplyr::count(CRM_PRODUCT,SEG)


TOTAL_CAMPAIGN_BASE %>% filter(SUBSEG != '4.SCH_INACTIVE') %>%
  dplyr::count(CRM_PRODUCT)

TOTAL_CAMPAIGN_BASE %>% filter(SUBSEG != '4.SCH_INACTIVE') %>%
  dplyr::summarise(n = n())

```

### ASSIGNING THE THRESHOLDS & OFFER AMOUNTS 

```{r}

TOTAL_CAMPAIGN_BASE_1 <- TOTAL_CAMPAIGN_BASE %>%
  filter(SUBSEG != '4.SCH_INACTIVE') %>%
  mutate(
         CUSTOMER_ID = CUST_ACCT_APPL_ID,
         THRESHOLD_CHECK = case_when(
           SUBSEG == "1.SCH_MORE_OVER_$500" ~ L6M_AVG_TXN_AMT+2000,
           SUBSEG == "2.SCH_MORE_UNDER_$500" ~ L6M_AVG_TXN_AMT+1000,
           SUBSEG == "3.SCH_LESS" ~ L6M_AVG_TXN_AMT+500,
      
         ),
          THRESHOLD = case_when(
             SUBSEG == "1.SCH_MORE_OVER_$500" ~ (round(round_any(L6M_AVG_TXN_AMT+2000,100,f=ceiling))),
           SUBSEG == "2.SCH_MORE_UNDER_$500" ~ (round(round_any(L6M_AVG_TXN_AMT+1000,100,f=ceiling))),
           SUBSEG == "3.SCH_LESS" ~ (round(round_any(L6M_AVG_TXN_AMT+500,100,f=ceiling))) ,
 
         ),
         OFFER = case_when( 
           SUBSEG == "1.SCH_MORE_OVER_$500" ~ "100",
           SUBSEG == "2.SCH_MORE_UNDER_$500" ~ "100",
           SUBSEG == "3.SCH_LESS" ~ "50",

         )
  ) %>%
  mutate(THRESHOLD = if_else(is.na(THRESHOLD)& SUBSEG == "1.SCH_MORE_OVER_$500", 2000, THRESHOLD )) %>%
   mutate(THRESHOLD = if_else(is.na(THRESHOLD)& SUBSEG == "2.SCH_MORE_UNDER_$500", 1000, THRESHOLD )) %>%
   mutate(THRESHOLD = if_else(is.na(THRESHOLD)& SUBSEG == "3.SCH_LESS", 500, THRESHOLD ))

range(TOTAL_CAMPAIGN_BASE_1$CRM_OTB_AMT)

TOTAL_CAMPAIGN_BASE_1 %>% filter(is.na(THRESHOLD)) %>%
  dplyr::count(CRM_PRODUCT, SUBSEG)

```
### FIXING THE CREDIT LIMIT 

#### 

```{r}

COUNT_OTB_CL_WASH <- TOTAL_CAMPAIGN_BASE_1 %>% 
  mutate( CREDITLIMIT_FLAG = case_when(
        THRESHOLD > CREDITLIMIT ~ "threshold > Cl",
        THRESHOLD > 6000 ~ "Spend threshold > 6000"
  ))

check_table <- table(COUNT_OTB_CL_WASH$SUBSEG, COUNT_OTB_CL_WASH$CREDITLIMIT_FLAG)
ftable(check_table)


TOTAL_CAMPAIGN_BASE_2 <- TOTAL_CAMPAIGN_BASE_1 %>%
   mutate(THRESHOLD = case_when(
        THRESHOLD <= 6000 ~ THRESHOLD, 
        THRESHOLD > 6000 ~ 6000,
        THRESHOLD > CREDITLIMIT ~ CREDITLIMIT,
  ),
        threshold_range = case_when (
          THRESHOLD <= 1000 ~ "$1000",
          THRESHOLD>1000 & THRESHOLD < 1200 ~ "$1001-$1199",
          THRESHOLD>=1200 & THRESHOLD < 1500 ~ "$1200-$1499",
          THRESHOLD>=1500 & THRESHOLD <= 1999 ~ "$1500-$2000",
          THRESHOLD>=2000 & THRESHOLD <= 3000 ~ "$2001-$3000",
          THRESHOLD>3000 & THRESHOLD <= 4000 ~ "$3001-$4000",
          THRESHOLD>4000 & THRESHOLD <= 6000 ~ "$4001-$6000",
          THRESHOLD > 6000 ~ "$6000+"
        ))


```

### PLOT ALL THE THRESHOLD RANGES 


```{r}
##str(TOTAL_CAMPAIGN_BASE_2)

#CHECK THE RANGE OF THE SPEND THRESHOLD

#dplyr::count(TOTAL_CAMPAIGN_BASE_2$CRM_PRODUCT)

# RANGE OF THE THRESHOLD 

#range(TOTAL_CAMPAIGN_BASE_2$CRM_OTB_AMT)

#range(TOTAL_CAMPAIGN_BASE_2$THRESHOLD)

## FREQ TABLE FOR THE SPEND THRESHOLD RANGE 
check_table_2 <- table(TOTAL_CAMPAIGN_BASE_2$SUBSEG, TOTAL_CAMPAIGN_BASE_2$threshold_range, TOTAL_CAMPAIGN_BASE_2$OFFER)
ftable(check_table_2)



ggplot(TOTAL_CAMPAIGN_BASE_2, aes(x=SUBSEG, fill = threshold_range))+
  geom_bar(position = "fill")+
  ylab("propotion")+coord_flip()+
     scale_fill_hue(c=45, l=80)+
          theme_bw()


TOTAL_CAMPAIGN_BASE_2 %>% filter(is.na(threshold_range)) %>%
      dplyr::count(CRM_PRODUCT, SUBSEG)
```
#### BUILDING THE CAMPAIGN DATA CONTROL GROUP AND OFFER_ACTIVATED_FLAG & SPEND_QUALIFIED_FLAG 

```{r}

PET_CA_936_NOV23_GOLDENQ <- sqldf(
  "
  SELECT CUSTOMER_ID
  ,CRM_PRODUCT
  ,CRM_PRODUCT_VARIANT
  ,SEG
  ,SUBSEG
  ,THRESHOLD
  ,OFFER
  ,'SG_CA_936_NOV23_GOLDENQ' as CAMPAIGN_ID
  ,	'2023-11-02' as  EXPIRY_DATE
  , '2023-11-01' as CAMPAIGN_START_DATE
  , '2023-11-30' as CAMPAIGN_END_DATE
  ,case when row_number() over (partition by SUBSEG order by random()) <=
                  0.1 * count(*) over (partition by SUBSEG) 
             then 'Y'
             else 'N'
             end as CONTROL_GROUP 
  ,'' as OFFER_ACTIVATED_FLAG
  ,''AS SPEND_QUALIFIED_FLAG
  FROM TOTAL_CAMPAIGN_BASE_2
  "
)

dim(TOTAL_CAMPAIGN_BASE_2)

dim(PET_CA_936_NOV23_GOLDENQ)

```


#### CHECK CONTROL_GROUP & SUBSEGS 

#### TOTAL ELIGIBLE FOR THE NOV23 CAMPAIGN 

```{r}
check_table_5 <- table(PET_CA_936_NOV23_GOLDENQ$SUBSEG, PET_CA_936_NOV23_GOLDENQ$CONTROL_GROUP)
ftable(check_table_5)

#count(PET_CA_936_NOV23_GOLDENQ$SUBSEG)
#count(PET_CA_936_NOV23_GOLDENQ$CRM_PRODUCT)


check_table_6 <- table(PET_CA_936_NOV23_GOLDENQ$OFFER_ACTIVATED_FLAG, PET_CA_936_NOV23_GOLDENQ$SPEND_QUALIFIED_FLAG)
ftable(check_table_6)
```
#### DISTRIBUTION BY CRM_PRODUCT, SEG, SUBSEG, OFFER & CONTROL_GROUP 

```{r}

## plots for the counts 

PLOTx <- PET_CA_936_NOV23_GOLDENQ %>%
          group_by(CRM_PRODUCT, CONTROL_GROUP)%>%
           dplyr::summarise(num = n(),
                            NUM_LEADS = comma(n()))

ggplot(PLOTx,aes(x= CRM_PRODUCT,y = num , fill = CONTROL_GROUP))+
            geom_bar(stat = "identity",position = "dodge")+
        scale_fill_brewer(palette="Spectral")+
          theme_bw()+
  geom_text(aes(label = NUM_LEADS),size = 2.5,position=position_dodge(width=0.9), vjust=-0.25)+
  labs(
    x = "Segments",
    y = "",
    fill = "CONTROL_GROUP"
        )



PLOTX1 <- PET_CA_936_NOV23_GOLDENQ %>%
          filter(CONTROL_GROUP == 'N') %>%
          group_by(CRM_PRODUCT,SEG)%>%
           dplyr::summarise(num = n(),
                            NUM_LEADS = comma(n()))

ggplot(PET_CA_936_NOV23_GOLDENQ, aes(x=CRM_PRODUCT, fill = SEG))+
  geom_bar(position = "fill")+
  ylab("propotion")+
     scale_fill_hue(c=45, l=80)+
          theme_bw()

#ggplot(PLOTX1,aes(x= CRM_PRODUCT,y = num , fill = SEG ))+
#            geom_bar(stat = "identity",position = "dodge")+
 #        scale_fill_brewer(palette="Spectral")+
      #    theme_bw()+
 # geom_text(aes(label = NUM_LEADS),size = 2.5,position=position_dodge(width=0.9), vjust=-0.25)+
 # labs(
   # x = "CRM_PRODUCT ",
   # y = "",
   # fill = "Segments"
 #       )


PLOT1 <- PET_CA_936_NOV23_GOLDENQ %>%
          filter(CONTROL_GROUP == 'N') %>%
          group_by(SUBSEG,SEG)%>%
           dplyr::summarise(num = n(),
                            NUM_LEADS = comma(n()))

ggplot(PET_CA_936_NOV23_GOLDENQ, aes(x=CRM_PRODUCT, fill = SUBSEG))+
  geom_bar(position = "fill")+
  ylab("propotion")+
     scale_fill_hue(c=45, l=80)+
          theme_bw()


#ggplot(PLOT1,aes(x= SUBSEG,y = num , fill = SEG))+
           # geom_bar(stat = "identity",position = "dodge")+
         #scale_fill_brewer(palette="Spectral")+
 #         theme_bw()+coord_flip()+
 # geom_text(aes(label = NUM_LEADS),size = 2.5,position=position_dodge(width=0.9), vjust=-0.25)+
 # labs(
  #  x = "Subsegs ",
  #  y = "",
    #fill = "Segments"
    #    )

PLOT2 <- PET_CA_936_NOV23_GOLDENQ %>%
            filter(CONTROL_GROUP == 'N') %>%
          group_by(SUBSEG,OFFER)%>%
           dplyr::summarise(num = n(),
                            NUM_LEADS = comma(n()))

ggplot(PLOT2,aes(x= SUBSEG,y = num , fill = OFFER))+
            geom_bar(stat = "identity",position = "dodge")+
         scale_fill_brewer(palette="Spectral")+
          theme_bw()+
  geom_text(aes(label = NUM_LEADS),size = 2.5,position=position_dodge(width=0.9), vjust=-0.25)+
  labs(
    x = "Subsegs",
    y = "",
    fill = "OFFER"
        )


```

#### TEST SEEDS TO GENERATE FOR OFFER_ACTIVATED_FLAG & SPEND_QUALIFIED_FLAG

```{r}

SEED_1 <- PET_CA_936_NOV23_GOLDENQ %>%
  arrange(desc(THRESHOLD)) %>%
  group_by(CRM_PRODUCT,CRM_PRODUCT_VARIANT,SEG, SUBSEG, CONTROL_GROUP) %>%
  slice(1) %>%
  mutate(
    OFFER_ACTIVATED_FLAG = case_when(
      CONTROL_GROUP == 'Y' ~ 'N',
      CONTROL_GROUP == 'N' ~ 'Y',
  
    ),
    SPEND_QUALIFIED_FLAG = case_when(
      CONTROL_GROUP == 'Y' ~ 'N',
      CONTROL_GROUP == 'N' ~ 'N',
    )
  )%>%
  ungroup()

shuffled_data= PET_CA_936_NOV23_GOLDENQ[sample(1:nrow(PET_CA_936_NOV23_GOLDENQ)), ]

SEED_2 <- shuffled_data %>%
  filter(CONTROL_GROUP == 'N') %>%
  group_by(CRM_PRODUCT,CRM_PRODUCT_VARIANT,SEG, SUBSEG) %>%
  slice(2) %>%
  mutate(
    OFFER_ACTIVATED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'Y',
    ),
    SPEND_QUALIFIED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'Y',
    )
  )%>%
  ungroup()

shuffled_data1 = PET_CA_936_NOV23_GOLDENQ[sample(1:nrow(PET_CA_936_NOV23_GOLDENQ)), ]


SEED_3 <- shuffled_data1 %>%
  filter(CONTROL_GROUP == 'N') %>%
  group_by(CRM_PRODUCT,CRM_PRODUCT_VARIANT,SEG, SUBSEG) %>%
  slice(1) %>%
  mutate(
    OFFER_ACTIVATED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'N',
    ),
    SPEND_QUALIFIED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'Y',
    )
  )%>%
  ungroup()

shuffled_data2 = PET_CA_936_NOV23_GOLDENQ[sample(1:nrow(PET_CA_936_NOV23_GOLDENQ)), ]

SEED_4 <- shuffled_data2 %>%
  filter(CONTROL_GROUP == 'N') %>%
  group_by(CRM_PRODUCT,CRM_PRODUCT_VARIANT,SEG, SUBSEG) %>%
  slice(1) %>%
  mutate(
    OFFER_ACTIVATED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'N',
    ),
    SPEND_QUALIFIED_FLAG = case_when(
      CONTROL_GROUP == 'N' ~ 'N',
    )
  )%>%
  ungroup()

SEEDS_TEST_DATA <- bind_rows(SEED_1,SEED_2,SEED_3,SEED_4)


## TABLE 6

#check_table_6 <- table(SEEDS_TEST_DATA$CONTROL_GROUP, SEEDS_TEST_DATA$OFFER_ACTIVATED_FLAG,
   #                    SEEDS_TEST_DATA$SPEND_QUALIFIED_FLAG)
#ftable(check_table_6)


#str(SEEDS_TEST_DATA)

```



```{r}

## for seeds 

PET_CA_936_SEEDS<- SEEDS_TEST_DATA %>% 
   dplyr::mutate(CUSTOMER_ID = paste("TEST", CRM_PRODUCT,"C360",row_number(),sep = "_") )
  
```

#### CREATING THE PRODUCTION DATA 

```{r}
PET_SG_CA936_NOV23_GOLDENQ <- bind_rows(PET_CA_936_NOV23_GOLDENQ,PET_CA_936_SEEDS)

str(PET_SG_CA936_NOV23_GOLDENQ)

PET_SG_CA936_NOV23_GOLDENQ %>% dplyr::count(CRM_PRODUCT)

PET_SG_CA936_NOV23_GOLDENQ %>% dplyr::count(CRM_PRODUCT,CONTROL_GROUP)

```

#### VOLUME IN TREATMENT GROUP BY CRM_PRODUCT SEG & SEBSEG 
```{r}
PET_SG_CA936_NOV23_GOLDENQ %>% filter(CONTROL_GROUP == 'N') %>% dplyr::count(CRM_PRODUCT,SEG,SUBSEG)
```

#### MAXIMUM THRESHOLD RANGE IN TREATMENT GROUP 
```{r}
range(PET_SG_CA936_NOV23_GOLDENQ$THRESHOLD)
# checking duplicates

PET_SG_CA936_NOV23_GOLDENQ %>% get_dupes(CUSTOMER_ID) %>% dplyr::summarize(n=n())
```


#### Transfering the PET back to snowflake


```{r}

table_id <- Id(database = Sys.getenv('CUSTOMER_ANALYTICS_WORKSPACE_DB'), schema = "CAMPAIGN_AUDIENCE", table = "PET_SG_CA936_NOV23_GOLDENQ")

dbWriteTable(myconn, table_id,PET_SG_CA936_NOV23_GOLDENQ, overwrite = TRUE)

```